---
title: "Journal 1"
#bibliography: references.bib
author: "Mylène Husson"
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
#rgl::setupKnitr()



colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```
```{r}
library(igraph)
```


Last compiled on `r format(Sys.time(), '%B, %Y')`
<br>

------------------------------------------------------------------------

# Week 2
<br>

------------------------------------------------------------------------

## Workshop

### Presenting my RQ's
Today I presented my various research questions and we discussed how to make them more concrete. I drew the network, and after a lot of discussion, I now understand how I could visualize the network I wanted to analyse. 

### Social networks in matrices
Next, with some help, I created a matrix filled with randomly assigned 0 and 1. Start coding in small steps: see what needs to happen, and create steps to get there. 


```{r}

# you can create 
# val2 <- sample(x = 0:1, size = 100*100, replace = TRUE, prob = c(0.8, 0.2))
# if you increase the probability of 1's then you have a higher density network

val <- sample(x = 0:1, size = 100*100, replace = TRUE)

mat = matrix(data = val, nrow = 100, ncol=100)
mat

# you can count how many ties a person has:
rowsums <- rowSums(mat)
rowsums

# you can see the percentage of 1's
rowmeans <- rowMeans(mat)
rowmeans
```


```{r}

# can say the diagonal needs to be a NA because people can't have ties with themselves it depends on the package you use whether you have to say NA or 0
diag(mat) <- NA
mat
```



```{r}
# you can also do it with for loops (more work)
# rep is replicate, is makkelijker dan typen
mat2 <- matrix(0, nrow = 100, ncol = 100)

for (col in 1:100) {
  for (row in 1:100) {
    mat2[row, col] <- sample(0:1, 1, replace = TRUE)
  }
}

mat2
```

```{r}
# if you want to have a symmetric matrix (undirexted network)
# need to be able to flip the rows and columns
val <- sample(x = 0:1, size = 100*100, replace = TRUE)

mat3 = matrix(data = val, nrow = 100, ncol=100)

# force symmetry
mat_sym <- (mat3 + t(mat3)) %% 2
mat_sym
#uses function upper triangle of the matrix

# you could also sum the networks: so if 1 knows 2 and 2 knows 1 they get a '2' 
# and then say all the 2's become 1's and all the 1's and 0's become 0's.
```
<br>

------------------------------------------------------------------------
Read Chapter 2 again: look at directional ties. Look at reciprocity.
How do you measure it?

reciprocity of network: number of reciprocal relations divided by the number of possible reciprocal ties
a possible reciprocal relationship is when at least one of the two people has a relationship with the other
because then it is possible for it to become reciprocal.

```{r}
val <- sample(x = 0:1, size = 4*4, replace = TRUE)

mat1 <- matrix(data = val, nrow = 4, ncol=4)
diag(mat1) <- 0
mat1

# transpose: make another matrix in which the columns and rows are switched
mat2 <- t(mat1)

# then add the networks so if there are two 1's so they become 2
mat3 <- mat1 + mat2
mat3

sum(mat3[upper.tri(mat3)] == 2)

# then divide by the number of possible reciprocal ties
# in this case there are 4 potential numbers 1/4 = 0.25
```

<br>

------------------------------------------------------------------------

### Chapter 2


You can describe networks by describing notes, the dyads, the egonets embedded in the network. And describing the network as a whole.

Multiplexity: the number of multiplex relationships/ possible number of multiplex relationships

Need to put the things that are in Chapter 2 in you theory section: show that you are familiar. 


Reformulate the questions for next week and keep it simple.Try to understand networks.
<br>

------------------------------------------------------------------------

### Chapter 4
Find the number of complete traids (= difficult).
The number of traids divided by the number of triads that could be closed.

```{r}
set.seed(123643)

net1 <- matrix(sample(0:1, 16, replace = TRUE), nrow=4, ncol=4)
net_un <- net1 + t(net1)
net_un[net_un ==2] <- 1
diag(net_un) <- 0
net_un

netg <- graph_from_adjacency_matrix(net_un)
netg
class(netg)
plot<- plot(netg)
plot

#igraph::transitivity(triads, type = "undirected")

# six closed ones: you count the closed ones three times, because there are three ways they could be 'unclosed'
# the unclosed ones: 2
# 6/2 = 3
```

For an egonet:
You can count the number of triads in an egonetwerk:
if there are none: the clustering = 0
if there is one out of three alters: the clustering = 1/3
High clustering (max = 1), can lead to higher stability of a network


Diad census!
```{r}
# Find out how many dyads census are in our matrix
# we need a directed network
diag(net1) <-0
neth <- graph_from_adjacency_matrix(net1)
dyad_census(neth)

plot1<- plot(neth)
plot1
# mut	  = the number of pairs with mutual connections = 3
# asym  = The number of pairs with non-mutual connections = 2
#null   = the number of pairs with no connection between them = 1

```
Triad census
```{r}
triad_census(neth)

# you get numbers for every kind of triangle (there are 16 kinds)
?triad_census
```

Reciprocity = reciprocated relations/ all possible reciprocated relations
```{r}
net1transp <- net1 + t(net1)
net1transp

numtwos <- sum(net1transp == 2)
numonetwos <- sum(net1transp == 1 | net1transp == 2)

reciprocity <- numtwos/numonetwos

reciprocity
```


<br>

------------------------------------------------------------------------

### Bram explains betweenness

How important certain actors are to get information across. You want to get information from actor A to actor B, and there are three shortest connections. For two of those connections C is necessary, you divided the amount of paths that go through C, by the total shortest paths: 2/3. It's always only about the shortest paths. If there is a direct connection between A to B, then C is not important at all.
You have to do it for all dyads in the network.

It is about 0/1 networks, not about weighted networks. 

<br>

------------------------------------------------------------------------

## Homework

Workshop/Homework:
1. Update your research questions
2. Start writing your introduction in which you discuss your RQs, the relevance of a social network perspective
3. Find one or two relevant papers with respect to your research question and focus on the type of data they use.
4. Make a list of the type of data you will need (actor attributes, relational attributes, etc.) in order to answer your RQs from a
social network perspective.
5. Update your lab journal / website

