---
title: "Journal 1"
#bibliography: references.bib
author: "Mylène Husson"
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
#rgl::setupKnitr()



colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

Last compiled on `r format(Sys.time(), '%B, %Y')`
<br>

------------------------------------------------------------------------

# Week 2
<br>

------------------------------------------------------------------------

## Workshop

Today I presented my various research questions and we discussed how to make them more concrete. I drew the network, and after a lot of discussion, I now understand how I could visualize the network I wanted to analyse. 

Next, with some help, I created a matrix filled with randomly assigned 0 and 1. Start coding in small steps: see what needs to happen, and create steps to get there. 


```{r}

# you can create 
# val2 <- sample(x = 0:1, size = 100*100, replace = TRUE, prob = c(0.8, 0.2))
# if you increase the probability of 1's then you have a higher density network

val <- sample(x = 0:1, size = 100*100, replace = TRUE)

mat = matrix(data = val, nrow = 100, ncol=100)
mat

# you can count how many ties a person has:
rowsums <- rowSums(mat)
rowsums

# you can see the percentage of 1's
rowmeans <- rowMeans(mat)
rowmeans
```


```{r}

# can say the diagonal needs to be a NA because people can't have ties with themselves it depends on the package you use whether you have to say NA or 0
diag(mat) <- NA
mat
```



```{r}
# you can also do it with for loops (more work)
# rep is replicate, is makkelijker dan typen
mat2 <- matrix(0, nrow = 100, ncol = 100)

for (col in 1:100) {
  for (row in 1:100) {
    mat2[row, col] <- sample(0:1, 1, replace = TRUE)
  }
}

mat2
```

```{r}
# if you want to have a symmetric matrix (undirexted network)
# need to be able to flip the rows and columns
val <- sample(x = 0:1, size = 100*100, replace = TRUE)

mat3 = matrix(data = val, nrow = 100, ncol=100)

# force symmetry
mat_sym <- (mat3 + t(mat3)) %% 2
mat_sym
#uses function upper triangle of the matrix

# you could also sum the networks: so if 1 knows 2 and 2 knows 1 they get a '2' 
# and then say all the 2's become 1's and all the 1's and 0's become 0's.
```
<br>

------------------------------------------------------------------------
Read Chapter 2 again: look at directional ties. Look at reciprocity.
How do you measure it?

reciprocity of network: number of reciprocal relations divided by the number of possible reciprocal ties
a possible reciprocal relationship is when at least one of the two people has a relationship with the other
because then it is possible for it to become reciprocal.

```{r}
val <- sample(x = 0:1, size = 4*4, replace = TRUE)

mat1 <- matrix(data = val, nrow = 4, ncol=4)
mat1

diag(mat1) <- 0
mat1

# transpose: make another matrix in which the columns and rows are switched
mat2 <- t(mat1)
mat2

# then add the networks so if there are two 1's so they become 2
mat3 <- mat1 + mat2
mat3

sum(mat3[upper.tri(mat3)] == 2)

# then divide by the number of possible reciprocal ties
# in this case there are 4 potential numbers 1/4 = 0.25




```

