---
title: "Journal 1"
#bibliography: references.bib
author: "Mylène Husson"
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
#rgl::setupKnitr()



colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

Last compiled on `r format(Sys.time(), '%B, %Y')`
<br>

------------------------------------------------------------------------

# Week 3
<br>

------------------------------------------------------------------------

## Workshop

Recap: people are connected through social networks and therefore the observations can't be seen as independent. The theoretical part is now completed. 

Now: what are the implications for the data

You can't ONLY study individuals, but also the relations: so now you, need data on relations. This means you always have to get information from atleast 2 people. 

