---
title: "Journal 1"
#bibliography: references.bib
author: "Mylène Husson"
---

```{r, echo=TRUE, results='hide', message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(scholar)
library(openalexR)
library(rvest)
library(jsonlite)
library(httr)
library(rvest)
library(reshape2)
library(xml2)
library(openxlsx)
library(polite)
library(igraph)
library(sna)
library(genderizeR)
library(RSelenium)
library(netstat)
library(pingr)

#load the functions you need from the packages
fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}

fsave <- function(x, file = NULL, location = "./data/processed/") {
  ifelse(!dir.exists("data"), dir.create("data"), FALSE)
  ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
  if (is.null(file))
    file = deparse(substitute(x))
  datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
  totalname <- paste(location, datename, file, ".rda", sep = "")
  save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
}

fload <- function(filename) {
  load(filename)
  get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
  knitr::kable(x, digits = 2, "html", ...) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
    kableExtra::scroll_box(width = "100%", height = "300px")
}

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

Last compiled on `r format(Sys.time(), '%B, %Y')`
<br>

------------------------------------------------------------------------

# Week 4
<br>

------------------------------------------------------------------------

## Workshop

Today we are going to look at network visualisation. It is important you look at the data

<br>

------------------------------------------------------------------------

###  Zachary’s karate club

```{r}
require(igraph)

# Visualise Zachary's network
g <- make_graph("Zachary")
plot(g)

# you see differences between ego's in centralities, it's a complete network, undirected and unweighted ties.
# Perhaps something like friendship or something.

gmat <- as_adjacency_matrix(g, type = "both", sparse = FALSE)
#gmat

# Descriptives
# number of nodes: vcount(g)

# number of edges: ecount(g)

# the number of degrees: heavliy skewed
igraph::degree(g)

# transitivity
# be aware that directed graphs are considered as undirected. but g is undirected.
igraph::transitivity(g, type = c("localundirected"), isolates = c("NaN", "zero"))

# betweenness: 1 and 34 very high
igraph::betweenness(g, directed = FALSE)

# dyad census: igraph::dyad.census(g)
# igraph::triad.census(g)
# I will use sna because it shows the names of the triads as well.

igraph::transitivity(g, type = "global")
#sna::gtrans(gmat)

triad_g <- data.frame(sna::triad.census(gmat))

# for transitivity on network level: divide number of transitive triads by all possible transitive triads

# X300 is the variable of transative triads, and the X201 is the one in which one person is linked with two persons, who are not linked: so it's a possible transitive triad. 
# therefore, X201 + X300 are all possible transititve triads.
transitivity_g <- (3 * triad_g$X300)/(triad_g$X201 + 3 * triad_g$X300)
transitivity_g
```
<br>
### Ashwin Presentation

You can look at network properties (descriptives, graph), Ashwin looks at how we can use networks to explain certain phenomena. 

RQ: How are social and intellectual relations structured and given shape within research universities?

Not only about social relationships, but also intellectual thinking.
Do shared interests lead to collaborations, or do collaborations lead to similar interests.

    - structure:    collaboration leads to similar interests
    - culture:      scientists with similar interests find each other
    - homophily:    similar backgrounds lead to similar interest and collaboration
    - propinquity:  physical proximity leads to similar research interest and collaboration

If you have a huge network of ties, you can see if there are people who do not work together with people you are observing, but that does not mean they don't collaborate at all. 

### Continuing with Zachary’s karate club

```{r}
# make sizes proportional to betweenness score
V(g)$size = igraph::betweenness(g, normalized = TRUE, directed = FALSE)* 60 + 10  #after some trial and error
plot(g, mode = "undirected")

# the + 10 is added because some nodes have a 0 on betweenness and dissapear in the graph without +10
# the * 60 makes the differences bigger

# now: we want no overlap 
set.seed(2345)
l <- layout_with_mds(g)  #https://igraph.org/r/doc/layout_with_mds.html
plot(g, layout = l)
# now you see three clusters: around 33/34, around 1 and around 3, and the cluser around 3 you didn't see before. And that the two biggest clusters are not linked directly.

# you can then say that specific ones should be further apart:
# l  #let us take a look at the coordinates
l[1, 1] <- 4
l[34, 1] <- -3.5
plot(g, layout = l)

# 1 and 34 are most connected, perhaps they are the owners/masters from the karate club
# and maybe they are having an argument and are therefore not connected
```

Looking at Jochem's paper about twitter and the people in parliament. 
You see pollarisation: people mostly interact with people in their own party (clusters)

<br>

------------------------------------------------------------------------

## Homework

Update your Research Questions

1. Visualize your social network data: Static (a) Interactive and/or dynamic (b)

2. Be prepared to discuss the results of your network visualization next week.

3. Continue writing your data section and your result section
4. Update your lab journal / website

<br>

------------------------------------------------------------------------

## Friday September 19th

<br>

------------------------------------------------------------------------

### Try assigning gender: 

```{r}
# from the tutorial
df <- fload(file = "./data/20230627df_names.rda")

firstname <- df |>
  distinct(firstname) |> #only unique
  select(firstname) |> #only this variable
  filter(firstname != "") |> #remove empty
  pull(firstname) #save as chr

test <- genderizeAPI(firstname[1])
#test$response

length(firstname)
df_genderizer <- data.frame(matrix(ncol = 4, nrow = length(firstname)))
colnames(df_genderizer) <- c("count", "name", "gender", "probability")

#for (i in 1:length(firstname)) {
#    Sys.sleep(0.1)
#    df_genderizer[i, ] <- genderizeAPI(firstname[i])$response
#}
#colnames(df_genderizer) <- c("count", "name", "gender", "probability")
#df_genderizer$name <- firstname  #so we know which names are not found. 

#df_genderizer

# now we have a probability score, but you can also dummify it
#df_genderizer <- df_genderizer[df_genderizer$probability > 0.9, ]

#df_genderizer <- subset(df_genderizer, select = c("name", "gender"))

#fshowdf(df_genderizer)
#View(df_genderizer)

#df |>
#    left_join(df_genderizer, by = c(firstname = "name")) -> df_gender

#fshowdf(df_gender)

#fsave(df_gender)

```
<br>
### Assigned gender
```{r}
# Rvest table object inspecteren en die geven aan het 
name = "Erik"

# Build URL robustly
base_url <- "https://nvb.meertens.knaw.nl/naam/is"
name_url <- paste0(base_url, "/", name)

table <- read_html(name_url) |>
  html_element("table") |>
  html_table()


# Replace "--" with "0" everywhere
table[table == "--"] <- "0"

# Now you can safely convert to numeric
val_male   <- as.numeric(table[2, 3])
val_female <- as.numeric(table[6, 3])

# Compare and assign gender
gender <- if (val_male > val_female) {
  "male"
} else if (val_female >= val_male) {
  "female"
} else {
  NA
}

gender

```
<br>
### Gender Function

```{r}

my_genderizer <- function(name) {
  name <- gsub("^/+|/+$", "", name)
  
  # Build URL
  base_url <- "https://nvb.meertens.knaw.nl/naam/is"
  name_url <- paste0(base_url, "/", name)
  
  # Try reading table
  table <- tryCatch(
    read_html(name_url) |>
      html_element("table") |>
      html_table(),
    error = function(e) NULL
  )
  
  if (is.null(table)) return(NA)  # return NA if no table found
  
  # Replace "--" with "0"
  table[table == "--"] <- "0"
  
  # Convert to numeric
  val_male   <- suppressWarnings(as.numeric(table[2, 3]))
  val_female <- suppressWarnings(as.numeric(table[6, 3]))
  
  # Decide gender
  if (is.na(val_male) & is.na(val_female)) {
    gender <- NA
  } else if (val_male > val_female) {
    gender <- "male"
  } else if (val_female > val_male) {
    gender <- "female"
  } else {
    gender <- NA
  }
  
  return(gender)
}

soc_pol <- readxl::read_excel("/Users/mylenehusson/Desktop/SocialNetworks/labjournal_mylene/data/20240419Scholarid_soc_pol.xlsx")
soc_pol_small <- soc_pol[1:20, ]
soc_pol_small$gender <- NA

soc_pol_small <- soc_pol_small |>
  mutate(firstname = word(Naam, 1)) 

for (i in seq_len(nrow(soc_pol_small))) {
  name <- soc_pol_small$firstname[i]
  gender <- my_genderizer(name)

  soc_pol_small$gender[i] <- gender
}

#View(soc_pol_small)
```
<br>
### The nomination Network

```{r}
# load in the data
scholars <- fload("./data/processed/scholars_20240924.rda")

# select scholars
# (sociology, RU)
demographics <- do.call(rbind.data.frame, scholars$demographics)
demographics <- demographics %>%
    mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
        is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
        ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
        is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))

sample <- which((demographics$Universiteit1.22 == "RU" | demographics$Universiteit2.22 == "RU" | demographics$Universiteit1.24 ==
    "RU" | demographics$Universiteit2.24 == "RU") & (demographics$discipline.22 == "sociology" | demographics$discipline.24 ==
    "sociology"))

demographics_soc <- demographics[sample, ]
scholars_sel <- lapply(scholars, "[", sample)

# construct the empty adjacency matrix
ids <- demographics_soc$au_id
wave2 <- wave1 <- matrix(0, nrow = length(ids), ncol = length(ids), dimnames = list(ids, ids))

# filter works
works <- scholars_sel$work

works_id <- unlist(lapply(works, function(l) l$id))
works_author <- unlist(lapply(works, function(l) l$author), recursive = FALSE)
works_year <- unlist(lapply(works, function(l) l$publication_year), recursive = FALSE)

df_works <- tibble(works_id, works_author, works_year)

dups <- which(duplicated(works_id))

df_works <- df_works[-dups, ]
df_works_w2 <- df_works[df_works$works_year > 2019, ]

# undirected
# undirected
for (i in 1:nrow(df_works_w2)) {
    egos <- df_works_w2$works_author[i][[1]]$au_id

    if (sum(ids %in% egos) > 0) {
        wave2[which(ids %in% egos), which(ids %in% egos)] <- 1
    }
}
```
<br>

Now one function to rule them all:

```{r}
fcolnet <- function(data = scholars, university = "RU", discipline = "sociology", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

    # step 1
    demographics <- do.call(rbind.data.frame, data$demographics)
    demographics <- demographics %>%
        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))

    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))

    demographics_soc <- demographics[sample, ]
    scholars_sel <- lapply(scholars, "[", sample)

    # step 2
    ids <- demographics_soc$au_id
    nwaves <- length(waves)
    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
        ids))
    dimnames(nets)

    # step 3
    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
        recursive = FALSE))

    df_works <- df_works[!duplicated(df_works), ]

    # step 4
    if (type == "first") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- df_works_w$works_author[i][[1]]$au_id[1]
                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "last") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "all") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                egos <- df_works_w$works_author[i][[1]]$au_id
                if (sum(ids %in% egos) > 0) {
                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
                }
            }
        }
    }
    output <- list()
    output$data <- scholars_sel
    output$nets <- nets
    return(output)
}
```

<br>
### Assigning Gender to demographics
```{r}

df_scholars <- do.call(rbind, scholars$demographics)

#View(df_scholars)

df_scholars2 <- df_scholars |>
  mutate(firstname = word(Naam, 1))  # extract first names

df_scholars2$gender <- NA_character_  # initialize gender column

for (i in seq_len(nrow(df_scholars2))) {
  name <- df_scholars2$firstname[i]
  gender <- my_genderizer(name)
  
  df_scholars2$gender[i] <- gender
  Sys.sleep(0.06)  # pause between requests
}

#View(df_scholars2)

```

<br>

------------------------------------------------------------------------

## Thursday Oktober 2nd

<br>

------------------------------------------------------------------------

### Add to big data

Now add the new demographics including gender to the big data

```{r}
fcolnet_gender <- function(data = scholars,
                           university = "RU",
                           discipline = "sociology",
                           waves = list(c(2015, 2018), c(2019, 2023)),
                           type = c("first"),
                           demographics = NULL) {
  
  # -------------------------
  # Step 1: demographics
  # -------------------------
  if (is.null(demographics)) {
    demographics <- do.call(rbind.data.frame, data$demographics)
  }
  
  demographics <- demographics %>%
    mutate(
      Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""),
      Universiteit2.22 = replace(Universiteit2.22, is.na(Universiteit2.22), ""),
      Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24), ""),
      Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""),
      discipline.22    = replace(discipline.22,    is.na(discipline.22),    ""),
      discipline.24    = replace(discipline.24,    is.na(discipline.24),    "")
    )
  
  sample <- which(
    (demographics$Universiteit1.22 %in% university |
       demographics$Universiteit2.22 %in% university |
       demographics$Universiteit1.24 %in% university |
       demographics$Universiteit2.24 %in% university) &
      (demographics$discipline.22 %in% discipline |
         demographics$discipline.24 %in% discipline)
  )
  
  demographics_soc <- demographics[sample, ]
  scholars_sel <- lapply(data, "[", sample)
  
  # -------------------------
  # Step 2: initialize network array
  # -------------------------
  ids <- demographics_soc$au_id
  nwaves <- length(waves)
  nets <- array(
    0,
    dim = c(nwaves, length(ids), length(ids)),
    dimnames = list(wave = 1:nwaves, ids, ids)
  )
  
  # -------------------------
  # Step 3: works dataframe
  # -------------------------
  df_works <- tibble(
    works_id     = unlist(lapply(scholars_sel$work, function(l) l$id)),
    works_author = unlist(lapply(scholars_sel$work, function(l) l$author), recursive = FALSE),
    works_year   = unlist(lapply(scholars_sel$work, function(l) l$publication_year), recursive = FALSE)
  )
  
  df_works <- df_works[!duplicated(df_works), ]
  
  # -------------------------
  # Step 4: build networks
  # -------------------------
  if (type == "first") {
    for (j in 1:nwaves) {
      df_works_w <- df_works[df_works$works_year >= waves[[j]][1] &
                               df_works$works_year <= waves[[j]][2], ]
      for (i in 1:nrow(df_works_w)) {
        ego <- df_works_w$works_author[i][[1]]$au_id[1]
        alters <- df_works_w$works_author[i][[1]]$au_id[-1]
        if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
          nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
        }
      }
    }
  }
  
  if (type == "last") {
    for (j in 1:nwaves) {
      df_works_w <- df_works[df_works$works_year >= waves[[j]][1] &
                               df_works$works_year <= waves[[j]][2], ]
      for (i in 1:nrow(df_works_w)) {
        ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
        alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
        if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
          nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
        }
      }
    }
  }
  
  if (type == "all") {
    for (j in 1:nwaves) {
      df_works_w <- df_works[df_works$works_year >= waves[[j]][1] &
                               df_works$works_year <= waves[[j]][2], ]
      for (i in 1:nrow(df_works_w)) {
        egos <- df_works_w$works_author[i][[1]]$au_id
        if (sum(ids %in% egos) > 0) {
          nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
        }
      }
    }
  }
  
  # -------------------------
  # Step 5: output
  # -------------------------
  output <- list()
  output$data <- scholars_sel
  output$nets <- nets
  output$demographics <- demographics_soc  # includes gender if passed in
  
  return(output)
}

```

```{r}
result_gender <- fcolnet_gender(
  data = scholars,
  university = "RU",
  discipline = "sociology",
  demographics = df_scholars2
  
)

# Now you can access gender info in the output
head(result_gender$demographics[, c("au_id", "firstname", "gender")])
```

### Visualisation

```{r}
# adjacency matrix for first wave, can get the second one by making it a 2
adj_mat <- result_gender$nets[1,,]

# create igraph object
g <- graph_from_adjacency_matrix(adj_mat, mode = "undirected")

# make sure vertex order matches demographics order
gender_vec <- result_gender$demographics$gender
names(gender_vec) <- result_gender$demographics$au_id

# assign gender attribute to igraph
V(g)$gender <- gender_vec[V(g)$name]

# I am not sure whether people with NA are still in my network so I added a grey option???
V(g)$color <- ifelse(V(g)$gender == "male", "blue",
                     ifelse(V(g)$gender == "female", "orange", "grey"))

# assign node size by betweenness centrality
V(g)$size <- igraph::betweenness(g, normalized = TRUE, directed = FALSE) * 60 + 7

# final plot
plot(
  g,
  vertex.label = NA,
  edge.arrow.size = 0.4,
  main = "Co-authorship Network RU Sociology (Wave 1)"
)

# add legend
legend(
  "topright",
  legend = c("Men", "Women", "Unknown"),
  col    = c("blue", "orange", "grey"),
  pch    = 19,
  pt.cex = 1.5,
  bty    = "n"
)
```

### Properties
```{r}

# number of nodes and edges
vcount(g)
ecount(g)

# density
edge_density(g)

# average degree
degree <- igraph::degree(g)
mean(degree)

# betweenness centrality
head(igraph::betweenness(g))

# transivitivity: clustering
transitivity(g, type = "global")


```
<br>

Let's if men or women have a higher degree of centrality:
```{r}
# degree of each node
deg <- igraph::degree(g, mode = "all") # for undirected

# gender attribute
gender <- V(g)$gender

# combine into a dataframe
network_df <- data.frame(
  au_id = V(g)$name,
  gender = gender,
  degree = deg
)

network_df |>
  group_by(gender) |>
  summarise(
    mean_degree = mean(degree),
    median_degree = median(degree),
    max_degree = max(degree),
    n = n()
  )

```
In this network, male scholars tend to have higher degree centrality than female scholars.

Many female nodes are isolated or weakly connected, while males have more collaborations.

<br>

### Updated RQ 

How does network centrality vary between men and women in Sociology and Political science departments in the Netherlands?

What is the correlation between a person’s centrality in a network and the number of citations that someone has in Sociology and Political science departments in the Netherlands?

How does network centrality influence the trajectory of citation growth over time, and is centrality more strongly associated with citation growth for women than for men in Sociology and Political science departments in the Netherlands?

<br>
Sketch of an introduction:

This paper analyses academic collaboration networks, where authors are represented as nodes and co-authored publications establish edges, forming an undirected network. I am particularly interested in understanding how the position of researchers within these networks, measured through centrality metrics, relates to academic recognition through citation impact.

In social network analysis (SNA), a node’s influence is commonly assessed using centrality metrics, including degree, betweenness, closeness, and eigenvector centrality (Freeman, 1980; Pappi & Scott, 1991; Xu & Chang, 2020). Authors occupying central positions tend to gain greater recognition and higher citation impact, linking network position directly to academic performance (Bihari & Pandia, 2015; Freeman, 1980).

Prior research suggests that gender plays a role in shaping network positions. Women often face structural barriers that limit centrality, though in certain contexts they can achieve equal or higher centrality by strategically forming collaborative ties (Burt, 1998; Brass, 1985; Kretschmer & Aguillo, 2005; Badar, Hite, & Badir, 2012). 

In the Netherlands, the social sciences are relatively gender-balanced, although men still frequently occupy higher organizational positions. This raises important questions about the distribution of centrality among male and female researchers and whether centrality confers similar advantages in terms of both citations and academic recognition.

By examining these dynamics, this study aims to shed light on how network position intersects with gender to influence academic performance, collaboration patterns, and visibility within scholarly communities.


References
Badar, K., Hite, J. M., & Badir, Y. F. (2012). Examining the relationship of co-authorship network centrality and gender on academic research performance: the case of chemistry researchers in Pakistan. Scientometrics, 94(2), 755–775. https://doi.org/10.1007/s11192-012-0764-z

Brass, D. J. (1985). Men’s and women’s networks: a study of interaction patterns and influence in an organisation. Academy Of Management Journal, 28(2), 327–343. https://doi.org/10.2307/256204

Burt, R. S. (1998). The gender of social capital. Rationality And Society, 10(1), 5–46. https://doi.org/10.1177/104346398010001001

Freeman, L. C. (1978). Centrality in social networks conceptual clarification. Social Networks, 1(3), 215–239. https://doi.org/10.1016/0378-8733(78)90021-7

Kretschmer, H., & Aguillo, I. F. (2005). New indicators for gender studies in Web networks. Information Processing & Management, 41(6), 1481–1494. https://doi.org/10.1016/j.ipm.2005.03.009

Pappi, F. U., & Scott, J. (1993). Social Network Analysis: A handbook. Contemporary Sociology A Journal Of Reviews, 22(1), 128. https://doi.org/10.2307/2075047

Xu, Q. A., & Chang, V. (2020). Co-authorship network and the correlation with academic performance. Internet Of Things, 12, 100307. https://doi.org/10.1016/j.iot.2020.100307

