---
title: "Journal 1"
#bibliography: references.bib
author: "Mylène Husson"
---

```{r, echo=TRUE, results='hide', message=FALSE, warning=FALSE}
library(knitr)
library(tidyverse)
library(scholar)
library(openalexR)
library(rvest)
library(jsonlite)
library(httr)
library(rvest)
library(reshape2)
library(xml2)
library(openxlsx)
library(polite)
library(igraph)
library(sna)
library(genderizeR)
library(RSelenium)
library(netstat)
library(pingr)
library(RSiena)
library(devtools)
library(RsienaTwoStep)

# load the functions you need from the packages
fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}

fsave <- function(x, file = NULL, location = "./data/processed/") {
  ifelse(!dir.exists("data"), dir.create("data"), FALSE)
  ifelse(!dir.exists("data/processed"), dir.create("data/processed"), FALSE)
  
  if (is.null(file)) {
    file <- deparse(substitute(x))
  }
  
  datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
  totalname <- paste(location, datename, file, ".rda", sep = "")
  save(x, file = totalname)  # need to fix if file is reloaded as input name, not as x.
}

fload <- function(filename) {
  load(filename)
  get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
  knitr::kable(x, digits = 2, "html", ...) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
    kableExtra::scroll_box(width = "100%", height = "300px")
}
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

Last compiled on `r format(Sys.time(), '%B, %Y')`
<br>

------------------------------------------------------------------------

## Week 5 Try outs
<br>

------------------------------------------------------------------------
### Define data: 

You have s501 at timepoint 1 and s502 for timepoint 2
Normally you will have to fix your data, but this data is already clean.

```{r}
?RSiena::s501

s501 #  network at timepoint 1
s502 # the network at timepoint 2

# dim(s501) shows the number of rows and the number of dimensions

# dimensions are the number of ros and the number of columns in your network, and we have 2 timepoints
net_soc_array <- array(data = c(s501, s502), dim = c(dim(s501), 2))

# dependent
net <- sienaDependent(net_soc_array)

```
<br>

## Include independent var
you can also include independent variable 

```{r}
s50a

# we have information on alcohol behaviour for 3 waves

alcohol <- s50a[,1]
alcohol

alcohol <- coCovar(alcohol) #say it's a time constant variable (I can do this with gender)
# only at time one, your alcohol score of T1 influences your T2

```
<br>

### combine into a dataset
```{r}

# Create siena data object
mydata <- sienaDataCreate(net, alcohol)
```
<br>
Below provides the Starting values: Includes basic rate parameter (shows you how many you need to get from one to another), outdegree, and reciprocity

```{r}
myeff <- getEffects(mydata)
myeff
```

We want more statistics in the model, can include many from a dataset. 
Can do it on your rate function, 
evaluation: the mechanisms for making are the same for breaking as for making  
(maybe considerations to make a tie to someone are different:  decisions to make a tie are different than to break a tie or create a tie, for instance: time investment may be important). 
endow: means making
creation: the costs of making 

We only use the evaluation function: mechanisms to make/ break a tie are similar. 

We should be able for each effect to calculate it for an ego given a network. 

In Chapter 12 are all the formula's (snijders siena Rsiena manual) [we will play around with those next week]

## Look at initial data DOES NOT WORK
```{r}
print01Report(mydata)
```

### Add effects
```{r}
# out act for instance meand: people who have many ties are likely to send more ties.
# you want to include that because tie distributions are skewed.
# can also campare in/out degrees. (these are control cariables to take into account the skeweness)


# inpop means: people who receive a lot of ties, are the people who receive a lot of ties at T2.
# the start degrees are 0 > no effect
myeff <- includeEffects(myeff, isolateNet, inPop, outAct)

```

### estimate
```{r}

# we need to define an algorithm saying how do we want to estimate the model
# for us it's not important, so leave it as it is. 
# then we say we are goiing to estimate it: siena07
# we are going to analyse it iwh my algorithm which we defined above, using mydata en myeff
# returnDeps = TRUE (for now not important, but it will be important when making goodness of fit measures)
myAlgorithm <- sienaAlgorithmCreate(projname = "test")
ansM1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
# if necessary estimate again!  ansM1 <- siena07(myAlgorithm, data = mydata, effects = myeff,
# prevAns = ansM1, returnDeps=TRUE)
ansM1

# look at other parameters.
```
On average 5.6 steps between agents, we see the eval out degree. 
Quite important reciprocity. 

For degree: negative means there is a density of less than .5

<br>

------------------------------------------------------------------------
## Homework

Make the data ready.
Re-read the manual
Pick one of the statistics in Chapter 12, which may be relevant for my project
And try to understand the function
and persent it next week

<br>

------------------------------------------------------------------------
## Friday Oktober 3rd

### Step 1
Getting started

scholars_20240924

```{r}
# load in the data
scholars <- fload("./data/processed/scholars_20240924.rda")

# select scholars
# (sociology, RU)
demographics <- do.call(rbind.data.frame, scholars$demographics)
demographics <- demographics %>%
    mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
        is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
        ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
        is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))

sample <- which((demographics$Universiteit1.22 == "RU" | demographics$Universiteit2.22 == "RU" | demographics$Universiteit1.24 ==
    "RU" | demographics$Universiteit2.24 == "RU") & (demographics$discipline.22 == "sociology" | demographics$discipline.24 ==
    "sociology"))

demographics_soc <- demographics[sample, ]
scholars_sel <- lapply(scholars, "[", sample)

# construct the empty adjacency matrix
ids <- demographics_soc$au_id
wave2 <- wave1 <- matrix(0, nrow = length(ids), ncol = length(ids), dimnames = list(ids, ids))

# filter works
works <- scholars_sel$work

works_id <- unlist(lapply(works, function(l) l$id))
works_author <- unlist(lapply(works, function(l) l$author), recursive = FALSE)
works_year <- unlist(lapply(works, function(l) l$publication_year), recursive = FALSE)

df_works <- tibble(works_id, works_author, works_year)

dups <- which(duplicated(works_id))

df_works <- df_works[-dups, ]
df_works_w2 <- df_works[df_works$works_year > 2019, ]

# undirected
# undirected
for (i in 1:nrow(df_works_w2)) {
    egos <- df_works_w2$works_author[i][[1]]$au_id

    if (sum(ids %in% egos) > 0) {
        wave2[which(ids %in% egos), which(ids %in% egos)] <- 1
    }
}

fcolnet <- function(data = scholars, university = "RU", discipline = "sociology", waves = list(c(2015,
    2018), c(2019, 2023)), type = c("first")) {

    # step 1
    demographics <- do.call(rbind.data.frame, data$demographics)
    demographics <- demographics %>%
        mutate(Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""), Universiteit2.22 = replace(Universiteit2.22,
            is.na(Universiteit2.22), ""), Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24),
            ""), Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""), discipline.22 = replace(discipline.22,
            is.na(discipline.22), ""), discipline.24 = replace(discipline.24, is.na(discipline.24), ""))

    sample <- which((demographics$Universiteit1.22 %in% university | demographics$Universiteit2.22 %in%
        university | demographics$Universiteit1.24 %in% university | demographics$Universiteit2.24 %in%
        university) & (demographics$discipline.22 %in% discipline | demographics$discipline.24 %in% discipline))

    demographics_soc <- demographics[sample, ]
    scholars_sel <- lapply(scholars, "[", sample)

    # step 2
    ids <- demographics_soc$au_id
    nwaves <- length(waves)
    nets <- array(0, dim = c(nwaves, length(ids), length(ids)), dimnames = list(wave = 1:nwaves, ids,
        ids))
    dimnames(nets)

    # step 3
    df_works <- tibble(works_id = unlist(lapply(scholars_sel$work, function(l) l$id)), works_author = unlist(lapply(scholars_sel$work,
        function(l) l$author), recursive = FALSE), works_year = unlist(lapply(scholars_sel$work, function(l) l$publication_year),
        recursive = FALSE))

    df_works <- df_works[!duplicated(df_works), ]

    # step 4
    if (type == "first") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- df_works_w$works_author[i][[1]]$au_id[1]
                alters <- df_works_w$works_author[i][[1]]$au_id[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "last") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
                alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
                if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
                  nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
                }
            }
        }
    }

    if (type == "all") {
        for (j in 1:nwaves) {
            df_works_w <- df_works[df_works$works_year >= waves[[j]][1] & df_works$works_year <= waves[[j]][2],
                ]
            for (i in 1:nrow(df_works_w)) {
                egos <- df_works_w$works_author[i][[1]]$au_id
                if (sum(ids %in% egos) > 0) {
                  nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
                }
            }
        }
    }
    output <- list()
    output$data <- scholars_sel
    output$nets <- nets
    return(output)
}

df_scholars <- do.call(rbind, scholars$demographics)

#View(df_scholars)

```

step 2: gender function
```{r}

my_genderizer <- function(name) {
  name <- gsub("^/+|/+$", "", name)
  
  # Build URL
  base_url <- "https://nvb.meertens.knaw.nl/naam/is"
  name_url <- paste0(base_url, "/", name)
  
  # Try reading table
  table <- tryCatch(
    read_html(name_url) |>
      html_element("table") |>
      html_table(),
    error = function(e) NULL
  )
  
  if (is.null(table)) return(NA)  # return NA if no table found
  
  # Replace "--" with "0"
  table[table == "--"] <- "0"
  
  # Convert to numeric
  val_male   <- suppressWarnings(as.numeric(table[2, 3]))
  val_female <- suppressWarnings(as.numeric(table[6, 3]))
  
  # Decide gender
  if (is.na(val_male) & is.na(val_female)) {
    gender <- NA
  } else if (val_male > val_female) {
    gender <- "male"
  } else if (val_female > val_male) {
    gender <- "female"
  } else {
    gender <- NA
  }
  
  return(gender)
}

soc_pol <- readxl::read_excel("/Users/mylenehusson/Desktop/SocialNetworks/labjournal_mylene/data/20240419Scholarid_soc_pol.xlsx")
soc_pol_small <- soc_pol[1:20, ]
soc_pol_small$gender <- NA

soc_pol_small <- soc_pol_small |>
  mutate(firstname = word(Naam, 1)) 

for (i in seq_len(nrow(soc_pol_small))) {
  name <- soc_pol_small$firstname[i]
  gender <- my_genderizer(name)

  soc_pol_small$gender[i] <- gender
}

#View(soc_pol_small)
```


step 3: add gender

```{r}

df_scholars2 <- df_scholars |>
  mutate(firstname = word(Naam, 1))  # extract first names

df_scholars2$gender <- NA_character_  # initialize gender column

for (i in seq_len(nrow(df_scholars2))) {
  name <- df_scholars2$firstname[i]
  gender <- my_genderizer(name)
  
  df_scholars2$gender[i] <- gender
  Sys.sleep(0.06)  # pause between requests
}

#View(df_scholars2)

fcolnet_gender <- function(data = scholars,
                           university = "RU",
                           discipline = "sociology",
                           waves = list(c(2015, 2018), c(2019, 2023)),
                           type = c("first"),
                           demographics = NULL) {
  
  # -------------------------
  # Step 1: demographics
  # -------------------------
  if (is.null(demographics)) {
    demographics <- do.call(rbind.data.frame, data$demographics)
  }
  
  demographics <- demographics %>%
    mutate(
      Universiteit1.22 = replace(Universiteit1.22, is.na(Universiteit1.22), ""),
      Universiteit2.22 = replace(Universiteit2.22, is.na(Universiteit2.22), ""),
      Universiteit1.24 = replace(Universiteit1.24, is.na(Universiteit1.24), ""),
      Universiteit2.24 = replace(Universiteit2.24, is.na(Universiteit2.24), ""),
      discipline.22    = replace(discipline.22,    is.na(discipline.22),    ""),
      discipline.24    = replace(discipline.24,    is.na(discipline.24),    "")
    )
  
  sample <- which(
    (demographics$Universiteit1.22 %in% university |
       demographics$Universiteit2.22 %in% university |
       demographics$Universiteit1.24 %in% university |
       demographics$Universiteit2.24 %in% university) &
      (demographics$discipline.22 %in% discipline |
         demographics$discipline.24 %in% discipline)
  )
  
  demographics_soc <- demographics[sample, ]
  scholars_sel <- lapply(data, "[", sample)
  
  # -------------------------
  # Step 2: initialize network array
  # -------------------------
  ids <- demographics_soc$au_id
  nwaves <- length(waves)
  nets <- array(
    0,
    dim = c(nwaves, length(ids), length(ids)),
    dimnames = list(wave = 1:nwaves, ids, ids)
  )
  
  # -------------------------
  # Step 3: works dataframe
  # -------------------------
  df_works <- tibble(
    works_id     = unlist(lapply(scholars_sel$work, function(l) l$id)),
    works_author = unlist(lapply(scholars_sel$work, function(l) l$author), recursive = FALSE),
    works_year   = unlist(lapply(scholars_sel$work, function(l) l$publication_year), recursive = FALSE)
  )
  
  df_works <- df_works[!duplicated(df_works), ]
  
  # -------------------------
  # Step 4: build networks
  # -------------------------
  if (type == "first") {
    for (j in 1:nwaves) {
      df_works_w <- df_works[df_works$works_year >= waves[[j]][1] &
                               df_works$works_year <= waves[[j]][2], ]
      for (i in 1:nrow(df_works_w)) {
        ego <- df_works_w$works_author[i][[1]]$au_id[1]
        alters <- df_works_w$works_author[i][[1]]$au_id[-1]
        if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
          nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
        }
      }
    }
  }
  
  if (type == "last") {
    for (j in 1:nwaves) {
      df_works_w <- df_works[df_works$works_year >= waves[[j]][1] &
                               df_works$works_year <= waves[[j]][2], ]
      for (i in 1:nrow(df_works_w)) {
        ego <- rev(df_works_w$works_author[i][[1]]$au_id)[1]
        alters <- rev(df_works_w$works_author[i][[1]]$au_id)[-1]
        if (sum(ids %in% ego) > 0 & sum(ids %in% alters) > 0) {
          nets[j, which(ids %in% ego), which(ids %in% alters)] <- 1
        }
      }
    }
  }
  
  if (type == "all") {
    for (j in 1:nwaves) {
      df_works_w <- df_works[df_works$works_year >= waves[[j]][1] &
                               df_works$works_year <= waves[[j]][2], ]
      for (i in 1:nrow(df_works_w)) {
        egos <- df_works_w$works_author[i][[1]]$au_id
        if (sum(ids %in% egos) > 0) {
          nets[j, which(ids %in% egos), which(ids %in% egos)] <- 1
        }
      }
    }
  }
  
  # -------------------------
  # Step 5: output
  # -------------------------
  output <- list()
  output$data <- scholars_sel
  output$nets <- nets
  output$demographics <- demographics_soc  # includes gender if passed in
  
  return(output)
}

```
Now let's try getting it
```{r}
result_gender <- fcolnet_gender(
  data = scholars,
  university = "RU",
  discipline = "sociology",
  demographics = df_scholars2,
  waves = list(c(2015, 2018), c(2019,2023)),
  type= c("first")
)

# Now you can access gender info in the output
head(result_gender$demographics[, c("au_id", "firstname", "gender")])

```

```{r}
wave1 <- result_gender$nets[1,,]
wave2 <- result_gender$nets[2,,]

# filter out the waves of the object: we need to check our input
dim(wave1)
dim(wave2)

# you need to have 0 missing values:
sum(is.na(wave1))
sum(is.na(wave2))

#check the diagonal: all 50 places should be 0
sum(diag(wave1)==0)
sum(diag(wave2)==0)

# everything should be 1 or 0:
sum(wave1>1)
sum(wave2>1)

# check if it's not empty: there are people with 1's
sum(wave1>0)
sum(wave2>0)


net_gender <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
# net_gender

# dependent
net2 <- sienaDependent(net_gender)

# independent variables
gender <- result_gender$demographics$gender

gender <- ifelse(gender=="female",1,0)
gender <- coCovar(gender)

#gender

# Create siena data object
mydata2 <- sienaDataCreate(net2, gender)
mydata2

```
### Step 2
Effects
```{r}
myeff <-getEffects(mydata2)
```
### Step 3
```{r}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)

print01Report(mydata2, modelname = "./results/soc_init")

```

### Step 4
do it yourselves

You have effects solely based on network structures, but you can also include effects based on ego characteristics: egox

ego x how many ties people send

egox = Vi (ego characteristic) * Xi+ (the degree)
if you have 2 ties and ego characteristics = 1 (hoogleraar)
egox = 1 * 2 = 2

alt x is if you receive ties

egox alt x effect: you sum egox and do that times Vj?
dan hou je rekening met homophily :)

```{r}

# delete eval from effect 
myeff <- includeEffects(myeff, egoX, interaction1 = "gender", type = "eval", include = F)   

# creation = maken
myeff <- setEffect(myeff, egoX, interaction1 = "gender", type = "creation", include = T)   

# endow = behouden
myeff <- setEffect(myeff, egoX, interaction1 = "gender", type = "endow", include = T)

# delete eval from effect inPop
myeff <- includeEffects(myeff, inPop, type = "eval", include = F)  

# inPop is indegree outAct is outdegree
myeff <- setEffect(myeff, inPop, type = "creation", include = T)
myeff <- setEffect(myeff, inPop, type = "endow", include = T)

# can allso add the altX to the equation
myeff <- setEffect(myeff, altX, interaction1 = "gender", include = F)  

# can also add egoXaltX
myeff <- setEffect(myeff, egoXaltX, interaction1 = "gender", include = T)


myeff <- includeInteraction(myeff, egoX, inPop, interaction1 = c("gender", ""), type = "eval", include = F)
myeff <- includeInteraction(myeff, egoX, inPop, interaction1 = c("gender", ""), type = "creation", include = T)
myeff <- includeInteraction(myeff, egoX, inPop, interaction1 = c("gender", ""), type = "endow", include = T)





```


### Step 5
Estimate

```{r}
myAlgorithm <- sienaAlgorithmCreate(projname = "soc_init")
ansM1 <- siena07(myAlgorithm, data = mydata2, effects = myeff, returnDeps = TRUE)
# if necessary estimate again!  ansM1 <- siena07(myAlgorithm, data = mydata, effects = myeff,
# prevAns = ansM1, returnDeps=TRUE)
ansM1
```
The convergence ratio is low, that's a good sign. This does not mean we have a good model. It does not say that the networks a similar, they are just similar on these two statistics. 

Vrouwen gaan over de tijd heen meer relaties aan dan mannen (ook behouden).
en dat weegt zwaarder dan dat ze relaties breken dan mannen. 

als je endow en creat apart aanzet:
zie je dat ze voornamelijk vaker ties behouden
en niet significant minder vaak ze crereeren 

eval indegree = significant: dus mensen die al veel hebben, trekken over tijd ook veel aan. 

if you look at egoXaltX and look at just egoX and altX:
women are more likely to send ties rather than receive ties :(


